Weakly Nonlinear Analysis of the Standard and Helical Magnetorotational Instabilities in a Taylor Couette Flow

### 2016-08-01 paper/widegap_mri_paper.tex
comparison of boundary layers in wide and narrow gap N31_B terms

@@

We examine the behavior of the wide gap MRI system as a function of $Pm$. Figure \ref{fig:coefficients} shows the critical parameters $k_c$ and $\reym$ as a function of $Pm$, as well as the coefficients $b$, $c$, and $d$. The GLE coefficients are remarkably insensitive to $Pm$. From Equation \ref{eq:gle} it is readily apparent that the saturation amplitude is $\alpha_{s} = \pm \sqrt{b/c}$, so we conclude that the saturation amplitude of the MRI is only very weakly dependent on $Pm$. This is in stark contrast to the narrow gap behavior of the system.

>>>>

\begin{figure*}
\centering
\includegraphics[width=\textwidth]{../figures/wide_narrow_gap_N31_B.pdf}
\caption{caption}\label{fig:wide_narrow_N31B}
\end{figure*}

@@

We examine the behavior of the wide gap MRI system as a function of $Pm$. Figure \ref{fig:coefficients} shows the critical parameters $k_c$ and $\reym$ as a function of $Pm$, as well as the coefficients $b$, $c$, and $d$. The GLE coefficients are remarkably insensitive to $Pm$. From Equation \ref{eq:gle} it is readily apparent that the asymptotic saturation amplitude is $\alpha_{s} = \pm \sqrt{b/c}$, so we conclude that the saturation amplitude of the MRI is only very weakly dependent on $Pm$. Note that because $\reym$ is essentially constant as a function of $Pm$, the saturation amplitude is equivalently insensitive to $\reye^{-1}$. This is in stark contrast to the narrow gap behavior of the system. For these same boundary conditions, \citeauthor{Umurhan:2007hs} (\citeyear{Umurhan:2007hs}) find that the narrow gap saturation amplitude scales as $Pm^{-4/3}$. They find that this amplitude dependence is driven by the $Pm^{1/3}$ dependence of the linear boundary layer. Boundary layer analysis similarly reveals a $\nu^{1/3}$ dependence for the radial extent of the boundary layer (\citei{Goodman:2002ix}). Why does the $Pm$ scaling of the boundary layer width not translate to a stronger $Pm$ scaling for the saturation amplitude in the wide gap case? The boundary layer in the wide gap case is strongly localized at the walls, i.e. $r_1$ and $r_2$.
